---
title: Model & Prediction
description:
toc: true
authors: []
tags: []
categories: []
series: []
date: 2022-12-12T19:58:14-05:00
lastmod: 2022-12-12T19:58:14-05:00
featuredVideo:
featuredImage:
draft: false
---

## Create training and testing datasets
```{r}
library(tidyverse)
Train <- read_csv(here::here("dataset","total.csv"),col_types = cols_only(Medicare_Coverage=col_number(),year=col_number(),LOS=col_number(),state=col_character()))
Train <- Train %>% filter(year==2019)
population_Train <- read_csv(here::here("dataset","population.csv"),col_types = cols_only(state=col_character(),Year2019=col_number()))
hs_Train <- read_csv(here::here("dataset","HS2019.csv"))
GDP_Train <- read_csv(here::here("dataset","GDP2019.csv"))
GPCI_Train <- read_csv(here::here("dataset","GPCI2019.csv"))
GPCI_Train<-GPCI_Train %>% group_by(state) %>% summarise(PW_GPCI=mean(PW_GPCI),PE_GPCI=mean(PE_GPCI),MP_GPCI=mean(MP_GPCI))
HCC_Train <- read_csv(here::here("dataset","HCC.csv"),col_types=cols_only(BENE_AVG_RISK_SCRE=col_number(),ACUTE_HOSP_READMSN_PCT=col_number(),state=col_character(),YEAR=col_number()))
HCC_Train <- na.omit(HCC_Train)
HCC_Train$state<-substr(HCC_Train$state,0,2)
HCC_Train<-HCC_Train %>% filter(YEAR==2019) %>% group_by(state) %>%  summarise(BENE_AVG_RISK_SCRE=mean(BENE_AVG_RISK_SCRE),ACUTE_HOSP_READMSN_PCT=mean(ACUTE_HOSP_READMSN_PCT))
df_list <- list(GPCI_Train,Train,hs_Train,GDP_Train,population_Train,HCC_Train)
Train <- df_list %>% reduce(full_join,by='state')
Train <- Train%>% select(PW_GPCI:Medicare_Coverage,status,GDP,Year2019,BENE_AVG_RISK_SCRE,ACUTE_HOSP_READMSN_PCT) %>% head(-3)
# GDP_Test <- read_csv(here::here("dataset","GDP.csv"))
# GPCI_Test <- read_csv(here::here("dataset","GPCI2020.csv"))
# hs_Test <- read_csv(here::here("dataset","HS2020.csv"))
# population_Test <- read_csv(here::here("dataset","population.csv"),col_types = cols_only(state=col_character(),Year2020=col_number()))
# LOS_Test <- read_csv(here::here("dataset","Avg_LOS.csv"))
# Medicare_Test <- read_csv(here::here("dataset","Medicare_data_sum.csv"),col_types = cols_only(state=col_character(),Medicare_Coverage=col_number()))
# df_list2 <- list(GPCI_Test,hs_Test,GDP_Test,population_Test,LOS_Test,Medicare_Test,Hcc_Test)
```

We first collect all out 2019 datasets and combine them together to create the trainning dataset called "Train".

##Create testing dataset
```{r}
Test <- read_csv(here::here("dataset","Data_Combined.csv"))
Test <- Test %>% select(BENE_AVG_RISK_SCRE:GDP,Medicare_Coverage:Year2020,Health_Status)
```

```{r}
library(GGally)
ggpairs(Train,upper = list(continuous = wrap("points", alpha = 0.3,size=0.1)),
        lower = list(continuous = wrap('cor', size = 4)))
```

We then create the scatterplot matrix of all the variables, figuring out which variables have the biggest correlation with Medicare_Coverage. According to the graph, Los seems like the one with the highest correlation.

```{r}
fit1 <- lm(Medicare_Coverage~.,data=Train)
summary(fit1)
```

We first fit a linear regression model on our output Medicare_Coverge with all other x variables, and get an Adjusted R-squared of 0.05534, which is a very low amount
```{r}
aic<-step(fit1,direction='both')
```

```{r}
fit2<-lm(Medicare_Coverage ~ LOS + BENE_AVG_RISK_SCRE + ACUTE_HOSP_READMSN_PCT,data=Train)
summary(fit2)
```

```{r}
sdres1 = rstandard(fit2)
yhat1 = fit2$fitted.values
plot(yhat1, sdres1)
```


```{r}
qqnorm(sdres1)
qqline(sdres1)
ggplot(data = data.frame(sdres1), aes(x = sdres1)) + geom_histogram(bins = 30) +
  ggtitle("Histogram MLS Plot")
```

```{r}
#Residual for training data
Resfit <- resid(fit2)
output1<-predict(fit2, se.fit = TRUE, newdata=data.frame(Test$BENE_AVG_RISK_SCRE,Test$LOS,Test$ACUTE_HOSP_READMSN_PCT))
Resfit2Validation <- Working2$Medicare_Coverage - output1$fit
mean((Resfit)^2)
mean((ResfitValidation)^2)
RMSE<-mean((ResfitValidation)^2) / mean((Test$Medicare_Coverage)^2)
```

```{r}
tested1 = data.frame(Test$Medicare_Coverage,output1$fit2, 1:length(output1$fit2));
ggplot(data = tested1, aes(x = Medicare_Coverage, y = Prediction_Medicare_Coverage)) + geom_point() + 
  geom_abline(intercept = 0, slope = 1) +
  ggtitle("Validation Medicare Coverage vs Prediction")
```